### 2019-12-17 defesa/tex/chapter/definicoes.tex
wip

    \caption{The ellipse as a parametric curve.}
    \input{tex/figures/ellipse_definition.tex}
    \fautor
    \label{fig:ellipse_params}
\end{figure}

@@

A non-axis-parallel ellipse centered at $c\in\R^2$ can also be described by \autoref{def:ellipse}. Nonetheless, a simpler equation is going to be used here. Besides the center, the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given. This angle represents the angle between the $x$-axis and the major-axis of the ellipse.

A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations. Reversing these transformations produces the following equation for a non-axis-parallel ellipse
\begin{equation}\label{eq:rotated_ellipse}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
\end{equation}
Also, the coverage region of an ellipse centered at $c\in\R^2$ with shape parameters $(a, b)\in\R^2_{>0}$ and rotation angle $\theta \in \R$ is represented by every point $(x, y) \in \R^2$ that satisfies \autoref{eq:rotated_ellipse_co} as follows
\begin{equation}\label{eq:rotated_ellipse_co}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1.
\end{equation}

An example of rotated ellipse can be seen on \autoref{fig:rotated_ellipse}. The dashed lines represent its major and minor axes which are rotated with respect to the coordinate axes.
On this picture, it is also displayed the symmetry of rotation angles regarding the ellipse's axes. From that, it can be seen that any angle of rotation $\theta$ is equivalent--as it produces the same ellipse--to the angle of rotation $\theta + k\pi$, with $k \in \mathbb{Z}$. Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.

@@

	\caption{A rotated ellipse.}
	\includegraphics[scale=.5]{tex/figures/rotated_ellipse}
	\fautor
	\label{fig:rotated_ellipse}
\end{figure}

>>>>

    \caption{The ellipse as a parametric curve.}
%    \input{tex/figures/ellipse_definition.tex}
   	\includegraphics[scale=.4]{tex/figures/ellipse_definition.pdf}
    \fautor
    \label{fig:ellipse_params}
\end{figure}

@@

A non-axis-parallel ellipse centered at $(c_x, c_y)\in\R^2$ can also be described by \autoref{def:ellipse}. Nonetheless, a simpler equation is going to be used here. Besides the center, and the shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$, an angle of rotation $\theta \in \R$ is given. This new parameter represents the angle between the $x$-axis and the major-axis of the ellipse, this can be seen on \autoref{fig:rotated_ellipse} where the dashed lines represent the ellipse's axes and the angle between the major-axis and the $x$-axis is displayed.

A rotated ellipse by $\theta$ can be transformed into a axis-parallel centered at the origin by applying two linear transformations: translation, so its center is at $(0, 0)$, then rotation so its major-axis is parallel to the $x$-axis. Reversing these transformations produces the following equation for a non-axis-parallel ellipse
\begin{equation}\label{eq:rotated_ellipse}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}=1.
\end{equation}
The coverage region of that same ellipse is given by every point $(x, y)\in\R^2$ that satisfies the following equation, which is the same as \autoref{eq:rotated_ellipse} with the equality sign $(=)$ replaced by $(\le)$
\begin{equation}\label{eq:rotated_ellipse_co}
\dfrac{((x-c_x)\cos\theta + (y-c_y)\sin\theta)^2}{a^2}+\dfrac{((x-c_x)\sin\theta - (y-c_y)\cos\theta)^2}{b^2}\le 1.
\end{equation}

Another important property of ellipses is shown on \autoref{fig:rotated_ellipse}. The two angles of rotation between the major-axis and the $x$-axis ($\theta$ and $\theta+\pi$) are actually equivalent--they produce the same ellipse. This symmetry is true for any angle of rotation, which means that $\theta$ is equivalent to $\theta+k\pi$, $k\in\mathbb{Z}$. Therefore, it is possible to conclude that to represent any ellipse, it is enough to specify the domain of $\theta$ to be $[0, \pi)$.

@@

	\caption{The rotated ellipse.}
	\includegraphics[scale=.38]{tex/figures/rotated_ellipse}
	\fautor
	\label{fig:rotated_ellipse}
\end{figure}

### 2019-12-17 defesa/tex/chapter/e3p.tex
wip

The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section. Even though its simple statement--it is short and uses only basic mathematical concepts--we were not able to find any work on it, or even on related problems. 
As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way. We try to give a review of some of those going through the issues with the failing approaches, at the end we propose a $\bigO(1)$ algorithm that finds every solution of the problem and run some numerical experiments to show the precision of the found solutions.

We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$. A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \tilde{E}(q, \theta)$.
The goal is to develop a method to find every solution of E3PNT.

@@

After that transformation, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$, such that the circle has radius $b$. Therefore, the only unknown of this problem is the angle of rotation. This idea reduces the number of variables from $3$ to only $1$, however, this would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.

>>>>

The problem of finding every center and angle of rotation of a fixed shape ellipse which makes it have three points on its border is presented in this section. Even though its simple statement--it is short and uses only basic mathematical concepts--we were not able to find any work on it, or even on related problems. 
As a result, starting from scratch, we ended up trying a handful of approaches with most of them failing on the way. We try to give a review of some of those, going through the issues with the failing ones. At the end we propose a $\bigO(1)$ algorithm that finds every solution of the problem, and also run some experiments to analyze efficiency in terms of numerical precision and CPU time.

We refer to this problem as \sigla{E3PNT}{Ellipse by Three points}, and an instance of it is given by three points $u, v, w \in \R^2$ and $E$, the coverage area of an ellipse with shape parameters $(a, b) \in \R^2_{>0}$, with $a > b$. A solution of E3PNT is a pair $(q, \theta) \in \R^2\times[0, \pi)$, such that $\{u, v, w\} \subset \partial E(q, \theta)$. Because of its application on \autoref{chapter:ellipses_n}, every solution of E3PNT must be encountered. This is a vital piece of information which makes this problem more challenging.

@@

After that transformation, the problem to be solved is finding a circumscribed circle of the triangle formed by the points $\{(0, 0), \varphi(v, \theta),\varphi(w, \theta)\}$, such that the circle's radius is $b$. Therefore, the only unknown of this problem is the angle of rotation. This idea reduces the number of variables from $3$ to only $1$, however, this would only be useful if checking the existence of a circumscribed circle with radius $b$ is a convenient problem.
